---
title: "Gun Control Chi-Square"
author: "Nelson Gould"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This: I'm Nelson and I am updating this markdown file here.

```{r}

library(tidyverse)
gc_df <- read_csv("gc_df.csv")

```

We are asking: Is there a significant difference in recommended gun control action for male and female respondents (should guns be easier, harder, or the same difficulty to get)?

Nelson: Data wrangling and counts

```{r}

get_guns <- gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender) 

rownames(get_guns) <- c("Female","Male")



```


My name is Maddie the amazing collaborator and I am doing a chi-squared test for independence!

We ask: "Is there a significant association between sex and opinion on whether guns should be more difficult, easier or the same difficulty to get?"


```{r}

# Let's look at the actual proportions

guns_prop <- prop.table(as.matrix(get_guns), 1)

#Run chi-square test for independence

guns_x2 <- chisq.test(get_guns)
guns_x2
```

"Recomended government action on gun access differed significantly between male (n = ) and female (n = ) respondents ($\chi^2$(`r guns_x2$parameter`) = ..., p <0.001). Notably, a much higher proportion of female respondents (57.4%) recommend making it more difficult to get guns, compared to 40.4% of male respondents. 